Supplementary material for ``An Efficient Forecasting Approach to Reduce Boundary Effects in Real-Time Time-Frequency Analysis''

### 2020-09-08 Notes/Supplementary material/SupMat.tex
proof

\subsubsection{Notations}
Considering $\bz\in\RR^N$ the deterministic signal defined in~\eqref{I-eq:sum.sine}, we denote by $\bz_k\in\RR^M$ the subsignal such that
\[
\bz_k[m] = \bz[N-K-M+k+m]\,,\quad \forall m\in\{0,\ldots,M-1\}\,,\ k\in\{0,\ldots,K\}\ .
\]
Define $\bZ\in\RR^{M \times K}$ and $\bZ'\in\RR^{M \times K}$, the matrices such that
\begin{align*}
\bZ &\defeq \begin{pmatrix}
\bz_0 & \cdots & \bz_{K-1}
\end{pmatrix}\\ 
\bZ' &\defeq \begin{pmatrix}
\bz_1 & \cdots & \bz_{K}
\end{pmatrix}\,.
\end{align*}
Let $\bD\in\RR^{M\times M}$ be the matrix defined by $\bD[m,m']=\delta_{m+1,m'}$.

Recall the model~\eqref{I-eq:model.noise}. Based on the definition of matrices $\bX$ and $\bY$, we have:
\begin{align}
\label{eq:XX.T}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T+\sigma^2\bI}_{\defeq S^{(0)}} + \bE^{(0)} \\
\label{eq:YX.T}
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ'\bZ^T +\sigma^2\bD}_{\defeq S^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} := \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$,
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.
We call $\bE^{(0)}$ and $\bE^{(1)}$ {\em error matrices} because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
Thus, the matrix $\tilde\bA$, defined in equation~\eqref{I-eq:lse}, is expressed in the form:
\begin{equation*}
\tilde\bA = (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\,.
\end{equation*}
Define $\bA_0$ the deterministic matrix such that
\begin{equation}
\bA_0 \defeq \bS^{(1)}{\bS^{(0)}}^\inv\,.
\label{eq:A0}
\end{equation}
We denote by $\balpha^{(\ell)}_0$ the last row of $\bA_0^\ell$. As a result, for $\ell\in \mathbb{N}^*$, the error vector $\bh^{(\ell)}$ defined by $\bh^{(\ell)}\defeq \balpha^{(\ell)} - \balpha^{(\ell)}_0$ satisfy the equation
\begin{align}
\nonumber
\bh^{(\ell)} &= \be_M^T\left(\tilde\bA^\ell-\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}

@@

\begin{lemma}[Expressions of $\bA_0$ and ${\bS^{(0)}}^{-1}$]
Let $\bS^{(0)}$ be the $M\times M$ matrices defined in~\eqref{eq:XX.T}. Let $\bA_0$ the $M\times M$ matrices defined in~\eqref{eq:A0}. Assume the deterministic signal $\bz$ takes the form~\eqref{I-eq:sum.sine}, and the observed noisy signal takes the form~\eqref{I-eq:model.noise}. Then, the matrix $\bS^{(0)}$ is given by
\begin{equation}
{\bS^{(0)}}^\inv[m,m']  = \dfrac1{\sigma^2}\delta_{m,m'}-\dfrac{2}{M\sigma^2}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\,,
\label{eq:S0.inv}
\end{equation}
and the matrix $\bA_0$ is given by
\begin{align}
\bA_0[m,m']  &= \delta_{m+1,m'} + \dfrac2M\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j\frac{m'}{M}\right)\delta_{m+1,M}\,.
\label{eq:A0.sine}
\end{align}
Let $\|\cdot\|_{\max}$ denote the maximum norm of a matrix, \ie~$\|\bM\|_{\max} = \max_{n,n'} \left|\bM[n,n']\right|$. Then,
\begin{align}
\label{eq:S0.inv.bound}
\left\|{\bS^{(0)}}^\inv\right\|_{\max} &\leq \dfrac1{\sigma^2}\left(1+\frac{2J}{M}\right)\,, \\
\left\|\bA_0\right\|_{\max} &\leq \max\left(1,\frac{2J}{M}\right)\ .
\label{eq:A0.bound}
\end{align}
\end{lemma}

\begin{proof}
It follows from the signal model~\eqref{I-eq:sum.sine} that matrices $\bS^{(0)}$ and $\bS^{(1)}$ take the following form:
\begin{align}
\nonumber
\bS^{(a)}[m,m'] &= \sigma^2\delta_{(m+a)m'}+\sum_{j,j'=1}^J\dfrac{\Omega_j\Omega_{j'}}{K}\sum_{k=0}^{K-1} \cos\left(2\pi \frac{f_j}{\fs}(N_0+m+a+k)+\varphi_j\right)\cos\left(2\pi \frac{f_{j'}}{\fs}(N_0+m'+k)+\varphi_{j'}\right) \\
\nonumber
&= \sigma^2\delta_{(m+a)m'}+\sum_{j=1}^J\dfrac{\Omega_j^2}{2K}\sum_{k=0}^{K-1} \cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right) + \cos\left(2\pi \frac{f_j}{\fs}(2k+m+a+m'+2N_0)\right)\\
\nonumber
&= \sigma^2\delta_{(m+a)m'}+\sum_{j=1}^J\Bigg( \dfrac{\Omega_j^2}2\cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right) + \dfrac{\Omega_j^2}{2K}\underbrace{\sum_{k=0}^{K-1}\cos\left(2\pi \frac{f_j}{\fs}(2k+m+a+m'+2N_0)\right)}_{=0\ \mathrm{because}\ \frac{f_j}\fs=\frac{p'_j}K } \Bigg)\\
&= \sigma^2\delta_{(m+a)m'}+\sum_{j=1}^J\dfrac{\Omega_j^2}2\cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right)\ .
\label{eq:S1}
\end{align}
Thus, $\bS^{(0)}$ is a circulant matrix, and is therefore diagonalizable in the Fourier basis:
\[
\bS^{(0)} = \bU\bLambda^{(0)}\bU^*\ ,
\]
where $\bU[m,m']=\frac1{\sqrt{M}}e^{-2\ii\pi mm'/M}$ and $\bLambda^{(0)} = \mathrm{diag}(\lambda_0^{(0)},\dots,\lambda_{M-1}^{(0)})$ with
\begin{align*}
\lambda_m^{(0)} &= \sigma^2 + \sum_{j=1}^J\dfrac{\Omega_j^2}2\sum_{q=0}^{M-1} \cos\left(2\pi\frac{f_j}{\fs} q\right) e^{-2\ii\pi qm/M} \\
&= \sigma^2 + \dfrac{M}{4}\sum_{j=1}^J\Omega_j^2(\delta_{m,p_j} + \delta_{m,M-p_j})\ .
\end{align*}
Therefore,
\begin{align*}
{\bS^{(0)}}^\inv  &= \bU{\bLambda^{(0)}}^\inv\bU^*\,,
\end{align*}
which leads to
\begin{equation*}
{\bS^{(0)}}^\inv[m,m']  = \dfrac1{\sigma^2}\delta_{m,m'}-\dfrac{2}{M\sigma^2}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\,.
\end{equation*}
Directly, we have:
\begin{align*}
\left|{\bS^{(0)}}^\inv[m,m']\right|  &= \dfrac1{\sigma^2}\left|\delta_{m,m'}-\dfrac{2}{M}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\right| \\
&\leq \dfrac1{\sigma^2}\left( 1+\dfrac{2}{M}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}} \right) \leq \dfrac1{\sigma^2}\left( 1+\dfrac{2J}{M} \right)\ .
\end{align*}
Thus, 
\[
\left\|{\bS^{(0)}}^\inv[m,m']\right\|_{\max}\leq\dfrac1{\sigma^2}\left( 1+\dfrac{2J}{M} \right)\ .
\]
Furthermore, combining equations~\eqref{eq:S1} and~\eqref{eq:S0.inv}, we have
\begin{align*}
\bA_0[m,m']  &= \sum_{q=0}^{M-1} {\bS^{(1)}}[m,q]{\bS^{(0)}}^\inv[q,m'] \\
&= \delta_{m+1,m'} + \dfrac2M\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j\frac{m'}{M}\right)\delta_{m+1,M}\,.
\end{align*}
Directly, we have:
\begin{align*}
\left|\bA_0[m,m']\right| &\leq \left\{
\begin{array}{ll}
1 & \mbox{if}\quad m<M-1\,, \\
\dfrac{2}{M}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}} & \mbox{if}\quad m=M-1\ . \\
\end{array}
\right.
\end{align*}
Thus, 
\[
\left\|\bA_0\right\|_{\max}\leq \max\left(1,\frac{2J}{M}\right)\ .
\]
\end{proof}

\begin{lemma}[Moments of $\bg$]
Let $\bg\in\RR^{M(M+1)}$ be the random vector defined in~\eqref{eq:vec}. Assume the deterministic signal $\bz$ takes the form~\eqref{I-eq:sum.sine}, and the observed noisy signal takes the form~\eqref{I-eq:model.noise}. Then, the second-order moments of $\bg$ are bounded as follows:
\begin{equation}
\left|\bE\{\bg[r]\bg[r']\}\right| \leq \dfrac1K \left( C_\bz^2\sigma^2 + 2 \sigma^4\right) + o\left(\dfrac1K\right)\,,\quad\forall (r,r')\in\{0,\ldots,M(M+1)-1\}^2\ ,
\label{eq:gg.bound}
\end{equation}
where $C_\bz \defeq 2\left(\sum_{j=1}^J \Omega_j\right)$. Besides, higher-order moments of $\bg$ behave as $o\left( \dfrac1K \right)$.
\end{lemma}

@@

\bg_1[r] &= \bE_1^{(a_r)}[m_r,m'_r] = \dfrac1K\sum_{k=0}^{K-1} \bz_k[m_r+a_r]\bw_k[m'_r] + \bw_k[m_r+a_r]\bz_k[m'_r] \\
\bg_2[r] &= \bE_2^{(a_r)}[m_r,m'_r] = \dfrac1K\sum_{k=0}^{K-1} \bw_k[m_r+a_r]\bw_k[m'_r] - \delta_{m_r+a_r,\,m'_r} \ ,

@@

Concerning higher-order moments, let $T\geq 3$ denote the order of the moment defined by $\EE\{\prod_{\theta=1}^T\bg[r_\theta]\}$. Thus,
\begin{align}
\nonumber
\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}& = \EE\left\{\prod_{\theta=1}^T \left(\sigma\bg_1[r_\theta] + \sigma^2\bg_2[r_\theta] \right)\right\}\\
\nonumber
&=\dfrac1{K^T}\EE\left\{\prod_{\theta=1}^T \left(\sum_{k=0}^{K-1}\rho_{\theta,k}(\bw[k+m'_{r_\theta}],\bw[k+m_{r_\theta}+a_{r_\theta}]) \right)\right\}\\ 
&=\dfrac1{K^T}\sum_{k_1=0}^{K-1}\cdots\sum_{k_T=0}^{K-1}\EE\left\{\prod_{\theta=1}^T \rho_{\theta,k_\theta}(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}]) \right\} \,,
\label{eq:multisum}
\end{align}
where
\[
\rho_{\theta,k}(u,v)=\sigma \bz_k[m_{r_\theta}+a_{r_\theta}]u + \sigma \bz_k[m'_{r_\theta}]v + \sigma^2uv - \delta_{m_{r_\theta}+a_{r_\theta},\,m'_{r_\theta}}\ .
\]
Thus,
\begin{align*}
\left|\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}\right| &\leq \dfrac{\nu_K}{K^T} C\ ,
\end{align*}
where
\[
C = \max_{(k_1,\ldots,k_T)} \left|\EE\left\{\prod_{\theta=1}^T \rho_{\theta,k_\theta}(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}]) \right\} \right| \,,
\]
and $\nu_K$ is the number of non-zero terms in the sum~\eqref{eq:multisum}. Note that $C$ is independent of $K$ (but depends on $\bz$ and $\sigma$). The behavior of the order $T$ moment in function of $K$ is therefore only determined by the ratio $\dfrac{\nu_K}{K^T}$.

Let us bound $\nu_K$. Fix $k_1$. For each of the other sum indexes $k_\theta$ ($\theta\in\{2,\ldots,T\}$), there are four values that make $\rho_{\theta,k_\theta}(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}])$ not independent of $\rho_{1,k_1}(\bw[k_1+m'_{r_1}],\bw[k_1+m_{r_1}+a_{r_1}])$. Indeed, since $\bw$ is a white noise these quantities are independent except when $k_\theta$ is such that:
\begin{align*}
k_\theta &= k_1+m'_{r_1}-m'_{r_\theta} \\
k_\theta &= k_1+m_{r_1}+a_{r_1} - m'_{r_\theta}\\
k_\theta &= k_1+m'_{r_1} - m_{r_\theta}- a_{r_\theta} \\
k_\theta &= k_1+m_{r_1}+a_{r_1} - m_{r_\theta}- a_{r_\theta}\ .
\end{align*}
Consequently, there exist at least $(K-4)^{T-1}$ combinations of $(k_2,\ldots,k_T)$ such that the correlation term given by $\EE\left\{\prod_{\theta=1}^T \rho_{\theta,k_\theta}(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}]) \right\}$ is zero. Because $T\geq 3$, we develop similar arguments on $k_2$ and $k_3$ to obtain the following maximum bound on the number of non-zero terms in the sum~\eqref{eq:multisum}:
\[
\nu_K\leq K^T - 3K(K-4)^{T-1} + 3K(K-4)(K-8)^{T-2}- K(K-4)(K-8)(K-12)^{T-3}\ .
\]
Thus,
\begin{align*}
\left|\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}\right| &\leq C \dfrac{K^T - 3K(K-4)^{T-1} + 3K(K-4)(K-8)^{T-2}- K(K-4)(K-8)(K-12)^{T-3}}{K^T} \\
&\leq C \left( 1 - 3\left(1-\frac4K\right)^{T-1} + 3\left(1-\frac4K\right)\left(1-\frac8K\right)^{T-2}- \left(1-\frac4K\right)\left(1-\frac8K\right)\left(1-\frac{12}{K}\right)^{T-3} \right) \\
&\leq C \left( 1 - 3 +\frac{12(T-1)}{K} + 3-\frac{12}K-\frac{24(T-2)}{K} -1 + \frac{4}K + \frac{8}K +\frac{12(T-3)}{K} + o\left(\dfrac1K\right)\right) \\
&\leq o\left(\dfrac1K\right)\ . \\
\end{align*}
Therefore,
\begin{equation*}
\left|\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}\right| = o\left(\dfrac1K\right)\,,\quad\forall T\geq 3\ .
\end{equation*}
\end{proof}

>>>>

\subsubsection{Notations}
Consider $\bz\in\RR^N$ the deterministic signal defined in~\eqref{I-eq:sum.sine}, and denote by $\bz_k\in\RR^M$ the subsignal such that
\[
\bz_k[m] = \bz[N-K-M+k+m]\,,\quad \forall m\in\{0,\ldots,M-1\}\,,\ k\in\{0,\ldots,K\}\ .
\]
Define $\bZ\in\RR^{M \times K}$ and $\bZ'\in\RR^{M \times K}$, the matrices such that
\begin{align*}
\bZ &\defeq \begin{pmatrix}
\bz_0 & \cdots & \bz_{K-1}
\end{pmatrix}\\ 
\bZ' &\defeq \begin{pmatrix}
\bz_1 & \cdots & \bz_{K}
\end{pmatrix}\,.
\end{align*}
Let $\bD\in\RR^{M\times M}$ be the matrix defined by $\bD[m,m']=\delta_{m+1,m'}$. Recall the model~\eqref{I-eq:model.noise}. Based on the definition of matrices $\bX$ and $\bY$, we have:
\begin{align}
\label{eq:XX.T}
\dfrac1K\bX\bX^T &= \underbrace{\dfrac1K\bZ\bZ^T+\sigma^2\bI}_{\defeq \bS^{(0)}} + \bE^{(0)} \\
\label{eq:YX.T}
\dfrac1K\bY\bX^T &= \underbrace{\dfrac1K\bZ'\bZ^T +\sigma^2\bD}_{\defeq \bS^{(1)}}+ \bE^{(1)} \ ,
\end{align}
where $\bE^{(a)} \defeq \sigma\bE_1^{(a)} + \sigma^2\bE_2^{(a)}$,
\[
\bE_1^{(a)}[m,m'] = \dfrac1K\sum_{k=0}^{K-1} \bz[N_0+m+a+k]\bw[N_0+m'+k] + \bw[N_0+m+a+k]\bz[N_0+m'+k]\ ,
\]
and
\[
\bE_2^{(a)}[m,m'] =  \dfrac1K\sum_{k=0}^{K-1} \bw[N_0+m+a+k]\bw[N_0+m'+k] - \delta_{(m+a)m'}\ ,
\]
with $a\in\{0,1\}$.
We call $\bE^{(0)}$ and $\bE^{(1)}$ {\em error matrices} because:
\begin{align*}
\EE\{\bE^{(0)}\} &= \EE\{\bE_1^{(0)}\} = \EE\{\bE_2^{(0)}\} = \bzero \\
\EE\{\bE^{(1)}\} &= \EE\{\bE_1^{(1)}\} = \EE\{\bE_2^{(1)}\} = \bzero\ .
\end{align*}
Thus, the random matrix $\tilde\bA$, defined in equation~\eqref{I-eq:lse}, is expressed in function of the above-defined matrices as:
\begin{equation*}
\tilde\bA = (\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\,.
\end{equation*}
Define $\bA_0$ the deterministic matrix such that
\begin{equation}
\bA_0 \defeq \bS^{(1)}{\bS^{(0)}}^\inv\,.
\label{eq:A0}
\end{equation}
We denote by $\balpha^{(\ell)}_0$ the last row of $\bA_0^\ell$. As a result, for $\ell\in \mathbb{N}^*$, the error vector $\bh^{(\ell)}$ defined by $\bh^{(\ell)}\defeq \balpha^{(\ell)} - \balpha^{(\ell)}_0$ satisfy the equation
\begin{align}
\nonumber
\bh^{(\ell)} &= \be_M^T\left(\tilde\bA^\ell-\bA_0^\ell\right) \\
&= \be_M^T\left(\left((\bS^{(1)}+\bE^{(1)})(\bS^{(0)}+\bE^{(0)})^\inv\right)^\ell- \bA_0^\ell\right)\ .
\label{eq:error.vec}
\end{align}

@@

\begin{lemma}[Expressions of $\bA_0$ and ${\bS^{(0)}}^{-1}$]
Let $\bS^{(0)}$ be the $M\times M$ matrix defined in~\eqref{eq:XX.T}. Let $\bA_0$ the $M\times M$ matrix defined in~\eqref{eq:A0}. Assume the deterministic signal $\bz$ takes the form~\eqref{I-eq:sum.sine}, and the observed noisy signal takes the form~\eqref{I-eq:model.noise}. Then, the inverse of the matrix $\bS^{(0)}$ is given by
\begin{equation}
{\bS^{(0)}}^\inv[m,m']  = \dfrac1{\sigma^2}\delta_{m,m'}-\dfrac{2}{M\sigma^2}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\,,
\label{eq:S0.inv}
\end{equation}
and the matrix $\bA_0$ is given by
\begin{align}
\bA_0[m,m']  &= \delta_{m+1,m'} + \dfrac2M\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j\frac{m'}{M}\right)\delta_{m+1,M}\,.
\label{eq:A0.sine}
\end{align}
Let $\|\cdot\|_{\max}$ denote the maximum norm of a matrix, \ie~$\|\bM\|_{\max} = \max_{n,n'} \left|\bM[n,n']\right|$. Then,
\begin{align}
\label{eq:S0.inv.bound}
\left\|{\bS^{(0)}}^\inv\right\|_{\max} &\leq \dfrac1{\sigma^2}\left(1+\frac{2J}{M}\right)\,, \\
\left\|\bA_0\right\|_{\max} &\leq \max\left(1,\frac{2J}{M}\right)\ .
\label{eq:A0.bound}
\end{align}
\end{lemma}

\begin{proof}
It follows from the signal model~\eqref{I-eq:sum.sine} that the matrices $\bS^{(0)}$ and $\bS^{(1)}$ take the following form:
\begin{align}
\nonumber
\bS^{(a)}[m,m'] &= \sigma^2\delta_{(m+a)\,,m'}+\sum_{j,j'=1}^J\dfrac{\Omega_j\Omega_{j'}}{K}\sum_{k=0}^{K-1} \cos\left(2\pi \frac{f_j}{\fs}(N_0+m+a+k)+\varphi_j\right)\cos\left(2\pi \frac{f_{j'}}{\fs}(N_0+m'+k)+\varphi_{j'}\right) \\
\nonumber
&= \sigma^2\delta_{(m+a)\,,m'}+\sum_{j=1}^J\dfrac{\Omega_j^2}{2K}\sum_{k=0}^{K-1} \cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right) + \cos\left(2\pi \frac{f_j}{\fs}(2k+m+a+m'+2N_0)\right)\\
\nonumber
&= \sigma^2\delta_{(m+a)\,,m'}+\sum_{j=1}^J\Bigg( \dfrac{\Omega_j^2}2\cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right) + \dfrac{\Omega_j^2}{2K}\underbrace{\sum_{k=0}^{K-1}\cos\left(2\pi \frac{f_j}{\fs}(2k+m+a+m'+2N_0)\right)}_{=0\ \mathrm{because}\ \frac{f_j}\fs=\frac{p'_j}K } \Bigg)\\
&= \sigma^2\delta_{(m+a)\,,m'}+\sum_{j=1}^J\dfrac{\Omega_j^2}2\cos\left(2\pi \frac{f_j}{\fs}(m+a-m')\right)\ .
\label{eq:S1}
\end{align}
Thus, $\bS^{(0)}$ is a circulant matrix, and is therefore diagonalizable in the Fourier basis:
\[
\bS^{(0)} = \bU\bLambda^{(0)}\bU^*\ ,
\]
where $\bU[m,m']=\frac1{\sqrt{M}}e^{-2\ii\pi mm'/M}$ and $\bLambda^{(0)} = \mathrm{diag}(\lambda_0^{(0)},\dots,\lambda_{M-1}^{(0)})$ with
\begin{align*}
\lambda_m^{(0)} &= \sigma^2 + \sum_{j=1}^J\dfrac{\Omega_j^2}2\sum_{q=0}^{M-1} \cos\left(2\pi\frac{f_j}{\fs} q\right) e^{-2\ii\pi qm/M} \\
&= \sigma^2 + \dfrac{M}{4}\sum_{j=1}^J\Omega_j^2(\delta_{m,p_j} + \delta_{m,M-p_j})\ .
\end{align*}
Therefore,
\begin{align*}
{\bS^{(0)}}^\inv  &= \bU{\bLambda^{(0)}}^\inv\bU^*\,,
\end{align*}
which leads to
\begin{equation}
{\bS^{(0)}}^\inv[m,m']  = \dfrac1{\sigma^2}\delta_{m,m'}-\dfrac{2}{M\sigma^2}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\,.
\label{eq:S0.inv.2}
\end{equation}
Directly, we have:
\begin{align*}
\left|{\bS^{(0)}}^\inv[m,m']\right|  &= \dfrac1{\sigma^2}\left|\delta_{m,m'}-\dfrac{2}{M}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j \dfrac{m-m'}{M}\right)\right| \\
&\leq \dfrac1{\sigma^2}\left( 1+\dfrac{2}{M}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}} \right) \leq \dfrac1{\sigma^2}\left( 1+\dfrac{2J}{M} \right)\ .
\end{align*}
Thus, 
\[
\left\|{\bS^{(0)}}^\inv[m,m']\right\|_{\max}\leq\dfrac1{\sigma^2}\left( 1+\dfrac{2J}{M} \right)\ .
\]
Furthermore, combining equations~\eqref{eq:S1} and~\eqref{eq:S0.inv.2}, we have
\begin{align*}
\bA_0[m,m']  &= \sum_{q=0}^{M-1} {\bS^{(1)}}[m,q]{\bS^{(0)}}^\inv[q,m'] \\
&= \delta_{m+1,m'} + \dfrac2M\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}}\cos\left(2\pi p_j\frac{m'}{M}\right)\delta_{m+1,M}\,.
\end{align*}
Directly, we have:
\begin{align*}
\left|\bA_0[m,m']\right| &\leq \left\{
\begin{array}{ll}
1 & \mbox{if}\quad m<M-1\,, \\
\dfrac{2}{M}\sum_{j=1}^J\dfrac{1}{1+\frac{4\sigma^2}{M\Omega_j^2}} & \mbox{if}\quad m=M-1\ . \\
\end{array}
\right.
\end{align*}
Thus, 
\[
\left\|\bA_0\right\|_{\max}\leq \max\left(1,\frac{2J}{M}\right)\ .
\]
\end{proof}

\begin{lemma}[Moments of $\bg$]
Let $\bg\in\RR^{M(M+1)}$ be the random vector defined in~\eqref{eq:vec}. Assume the deterministic signal $\bz$ takes the form~\eqref{I-eq:sum.sine}, and the observed noisy signal takes the form~\eqref{I-eq:model.noise}. Then, as $K\to\infty$, the second-order moments of $\bg$ are bounded as follows:
\begin{equation}
\left|\bE\{\bg[r]\bg[r']\}\right| \leq \dfrac1K \left( C_\bz^2\sigma^2 + 2 \sigma^4\right) + o\left(\dfrac1K\right)\,,\quad\forall (r,r')\in\{0,\ldots,M(M+1)-1\}^2\ ,
\label{eq:gg.bound}
\end{equation}
where $C_\bz \defeq 2\left(\sum_{j=1}^J \Omega_j\right)$. Besides, higher-order moments of $\bg$ behave as $o\left( \dfrac1K \right)$.
\end{lemma}

@@

\bg_1[r] &= \bE_1^{(a_r)}[m_r,m'_r] = \dfrac1K\sum_{k=0}^{K-1} \bz_k[m_r+a_r]\bw_k[m'_r] + \bw_k[m_r+a_r]\bz_k[m'_r]\,, \\
\bg_2[r] &= \bE_2^{(a_r)}[m_r,m'_r] = \dfrac1K\sum_{k=0}^{K-1} \bw_k[m_r+a_r]\bw_k[m'_r] - \delta_{m_r+a_r,\,m'_r} \,,

@@

Concerning higher-order moments, let $T\geq 3$ denote the order of the moment defined by $\EE\{\prod_{\theta=1}^T\bg[r_\theta]\}$. Thus,
\begin{align}
\nonumber
\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}& = \EE\left\{\prod_{\theta=1}^T \left(\sigma\bg_1[r_\theta] + \sigma^2\bg_2[r_\theta] \right)\right\}\\
\nonumber
&=\dfrac1{K^T}\EE\left\{\prod_{\theta=1}^T \left(\sum_{k=0}^{K-1}\rho_{\theta,k}\left(\bw[k+m'_{r_\theta}],\bw[k+m_{r_\theta}+a_{r_\theta}]\right) \right)\right\}\\ 
&=\dfrac1{K^T}\sum_{k_1=0}^{K-1}\cdots\sum_{k_T=0}^{K-1}\EE\left\{\prod_{\theta=1}^T \rho_{\theta,k_\theta}\left(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}]\right) \right\} \,,
\label{eq:multisum}
\end{align}
where
\[
\rho_{\theta,k}(u,v)=\sigma \bz_k[m_{r_\theta}+a_{r_\theta}]u + \sigma \bz_k[m'_{r_\theta}]v + \sigma^2uv - \delta_{m_{r_\theta}+a_{r_\theta},\,m'_{r_\theta}}\ .
\]
Thus,
\begin{equation*}
\left|\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}\right| \leq \dfrac{\nu_K}{K^T} C_T\ ,
\end{equation*}
where
\[
C_T = \max_{(k_1,\ldots,k_T)} \left|\EE\left\{\prod_{\theta=1}^T \rho_{\theta,k_\theta}(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}]) \right\} \right| \,,
\]
and $\nu_K$ is the number of non-zero terms in the sum~\eqref{eq:multisum}. Note that $C_T$ is independent of $K$ (but depends on $\bz$ and $\sigma$). The behavior of the order $T$ moment in function of $K$ is therefore only determined by the ratio $\dfrac{\nu_K}{K^T}$.

Let us bound $\nu_K$. Fix $k_1$. For each of the other indexes of summation $k_\theta$ ($\theta\in\{2,\ldots,T\}$), there are four values that make $\rho_{\theta,k_\theta}(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}])$ not independent of $\rho_{1,k_1}(\bw[k_1+m'_{r_1}],\bw[k_1+m_{r_1}+a_{r_1}])$. Indeed, since $\bw$ is a white noise these quantities are independent except when $k_\theta$ is such that:
\begin{align*}
k_\theta &= k_1+m'_{r_1}-m'_{r_\theta} \\
k_\theta &= k_1+m_{r_1}+a_{r_1} - m'_{r_\theta}\\
k_\theta &= k_1+m'_{r_1} - m_{r_\theta}- a_{r_\theta} \\
k_\theta &= k_1+m_{r_1}+a_{r_1} - m_{r_\theta}- a_{r_\theta}\ .
\end{align*}
Consequently, for each value of $k_1$ there exist at least $(K-4)^{T-1}$ combinations of $(k_2,\ldots,k_T)$ such that the correlation term given by $\EE\left\{\prod_{\theta=1}^T \rho_{\theta,k_\theta}(\bw[k_\theta+m'_{r_\theta}],\bw[k_\theta+m_{r_\theta}+a_{r_\theta}]) \right\}$ is zero. Because $T\geq 3$, we develop similar arguments on $k_2$ and $k_3$ to obtain the following maximum bound on the number of non-zero terms in the sum~\eqref{eq:multisum}:
\[
\nu_K\leq K^T - 3K(K-4)^{T-1} + 3K(K-4)(K-8)^{T-2}- K(K-4)(K-8)(K-12)^{T-3}\ .
\]
Thus,
\begin{align*}
\left|\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}\right| &\leq C_T \dfrac{K^T - 3K(K-4)^{T-1} + 3K(K-4)(K-8)^{T-2}- K(K-4)(K-8)(K-12)^{T-3}}{K^T} \\
&\leq C_T \left( 1 - 3\left(1-\frac4K\right)^{T-1} + 3\left(1-\frac4K\right)\left(1-\frac8K\right)^{T-2}- \left(1-\frac4K\right)\left(1-\frac8K\right)\left(1-\frac{12}{K}\right)^{T-3} \right) \\
&\leq C_T \left( 1 - 3 +\frac{12(T-1)}{K} + 3-\frac{12}K-\frac{24(T-2)}{K} -1 + \frac{4}K + \frac{8}K +\frac{12(T-3)}{K} + o\left(\dfrac1K\right)\right) \\
&\leq C_T\ o\left(\dfrac1K\right)\ . \\
\end{align*}
Therefore,
\begin{equation*}
\left|\EE\left\{\prod_{\theta=1}^T\bg[r_\theta]\right\}\right| = o\left(\dfrac1K\right)\,,\quad\forall T\geq 3\ .
\end{equation*}
\end{proof}
